---
title: "2018-12-07 Hearthstone Probability"
author: "zpb"
date: "December 7, 2018"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#The Scenario
At 9:18 seconds in this youtube video https://youtu.be/FcabbroD2mE?t=558 the opponent casts a Holy Wrath which sends out 8 bolts that can hit any opposing character. For our hero to win, he needs it to miss his Hellfiend, which has 5 HP. His hero has 24, and his Lakkari Felhound has 6 HP. This is very unlikely, right? Let's run a simulation to find out just how unlikely it is!

I am using the video https://www.youtube.com/watch?v=pBGMt28xgvk as a guide to help me create this simulation. If I struggle too much I'll give up lol, but I think this is a decent place to start.

#Simulation
There is something deceiving in this simulation. I was naive and though that I don't need to worry about having to set limits on how high we can let the Lakkari Felhound's damage get, but I was wrong because it has 6 health. Also  Similarly with the hero having >8 health. Doggone it. I had to write some if() statements that helped clear this up!

Using summarize(mtibble, mean(Hellfiend >= 6)) these are 1.97% of cases if we don't remove them. That's quite a lot in my book.

```{r}
library(tidyverse)

#Column 1 is the Hellfiend, Column 2 is the Lakkari Felhound, Column 3 is the hero
#Every row of the matrix is a run of the simulation
#Run 1.5 million repeats of this and then find the % of them that do not have any damage on the hellfiend
#Avoid doing >6 damage to the Lakkari Felhound and >5 to the Hellfiend

trial <- 1.5e6L

m <- matrix(0L, nrow = trial, ncol = 3L)

for (i in 1:trial){
    for (attack in 1:8) {
        target <- sample(1:3, 1)
        m[i, target] <- m[i, target] + 1 
        if(m[i, 2] > 6){ 
            m[i, 2] <- m[i, 2] - 1 
            newtarget1 <- sample(c(1,3), 1)
            m[i, newtarget1] <- m[i, newtarget1] + 1 
            }
        if(m[i, 1] > 5){
            m[i, 1] <- m[i, 1] - 1
            newtarget2 <- sample(c(2,3), 1)
            m[i, newtarget2] <- m[i, newtarget2] + 1
            }
        }   
    }   

#Put that matrix m into a tibble so we can summarize it and also remove all of the outcomes that aren't possible
#i.e. all outcomes where Hellfiend takes more than 5 damage or the Lakkari Felhound takes more than 6

mtibble <- m %>%
  as_tibble(m) %>%
  rename("Hellfiend" = "V1",
         "Lakkari_Felhound" = "V2",
         "Hero" = "V3")

summarize(mtibble,
          pct_win = mean(Hellfiend == 0),
          max_LF = max(Lakkari_Felhound),
          max_HF = max(Hellfiend),
          max_hero = max(Hero))
```


#Result

Looks like there was ~3.8% chance of that happening. Quite lucky!