---
title: "2018-12-07 Hearthstone Probability"
author: "zpb"
date: "December 7, 2018"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#This code as of now is incorrect
I naively allowed the situation to exist where Lakkari dies and the subsequent damage event was not rerolled. Back to the drawing board!

#The Scenario
At 9:18 seconds in this youtube video https://youtu.be/FcabbroD2mE?t=558 the opponent casts a Holy Wrath which sends out 8 bolts that can hit any opposing character. For our hero to win, he needs it to miss his Hellfiend, which has 5 HP. His hero has 24, and his Lakkari Felhound has 6 HP. This is very unlikely, right? Let's run a simulation to find out just how unlikely it is!

I am using the video https://www.youtube.com/watch?v=pBGMt28xgvk as a guide to help me create this simulation. If I struggle too much I'll give up lol, but I think this is a decent place to start.

#Simulation
There is something deceiving in this simulation. I was naive and though that I don't need to worry about having to set limits on how high we can let the Lakkari Felhound's damage get, but I was wrong because it has 6 health. Also  Similarly with the hero having >8 health. Doggone it.

Using summarize(mtibble, mean(Hellfiend >= 6)) these are 1.97% of cases. Not completely insignificant.

```{r}
library(tidyverse)

#Column 1 is the Hellfiend, Column 2 is the Lakkari Felhound, Column 3 is the hero
#Every row of the matrix is a run of the simulation
#Run 1.5 million repeats of this and then find the # of them that do not have any damage on the hellfiend

repeats <- 1.5e6L

m <- matrix(0L, nrow = repeats, ncol = 3L)

for (trials in 1:repeats){
  for (j in 1:8) {
    target <- sample(3, 1)
    m[trials, target] <- m[trials, target] + 1L
  }
}

#Put that matrix m into a tibble so we can summarize it and also remove all of the outcomes that aren't possible
#i.e. all outcomes where Hellfiend takes more than 5 damage or the Lakkari Felhound takes more than 6

mtibble <- m %>%
  as_tibble(m) %>%
  rename("Hellfiend" = "V1",
         "Lakkari_Felhound" = "V2",
         "Hero" = "V3") %>%
  filter(Hellfiend <= 5 & Lakkari_Felhound <= 6) #this is the illegal part. This is really dumb and isn't allowed. You need to figure out how to reroll the situations where Lakkari Felhound takes more than 6 damage and have it only select between Hellfiend and Hero.

summarize(mtibble,
          mean(Hellfiend == 0))
```


#Result

Looks like in the siuation I simulated (which is surprisingly close to the real situation, BUT ISN'T) there was ~3.85% chance of that happening. Quite lucky! BUT WRONG!